
The most important task in order to implement our project is the infrastructure, without it our project wouldn't work. The basic infrastructure will be our first concern, namely the Web Server configuration, ICE and signaling servers. 

The Web development can only start after the basic infrastructure configuration. When leading with streams, the infrastructure will be complemented with stream servers.

There will be four prototypes, the first one should implement most of streaming and collaborative functionalities. The second prototype will have the same functionalities but a more friendly user interface which will be tested and reviewed by potential users. The third prototype will be an improvement based on the users feedback. In the final prototype we will improve our system performance. 


\tikzset{every picture/.style={xscale=0.49,yscale=0.55,transform shape}}

\begin{ganttchart}[vgrid, hgrid]{1}{36}
\gantttitle{2015}{28}
\gantttitle{2016}{8} \\
\gantttitle{Jun}{4}
\gantttitle{Jul}{4}
\gantttitle{Aug}{4}
\gantttitle{Sep}{4}
\gantttitle{Oct}{4}
\gantttitle{Nov}{4}
\gantttitle{Dec}{4}
\gantttitle{Jan}{4}
\gantttitle{Feb}{4} \\
\gantttitlelist{1,...,36}{1}\\
%First Group
\ganttgroup{Thesis}{1}{35} \\
\ganttbar{Related work evaluation}{1}{30}\\
\ganttbar{Thesis writing}{19}{35} \\
\ganttbar{Paper writing}{25}{35} \\
\ganttmilestone{Delivery}{35}{35} \\
%\ganttlink{elem0}{elem1}
%\ganttgroup{Resume}{1}{10} \\

%\ganttmilestone{Milestone 1}{11}
%Second Group
\ganttgroup{Implementation}{1}{1}\ganttgroup{}{4}{8}\ganttgroup{}{11}{26}\ganttgroup{}{29}{30} \\
\ganttbar{Basic configuration}{1}{1} \\
%\ganttlink{elem4}{elem5}
%\ganttmilestone{Milestone 1}{11}
%Third Group
\ganttbar{WebRTC basics}{4}{4} \\
\ganttbar{Video \& Audio Communication}{4}{5} \\
\ganttbar{Non-Interactive Record \& Playback}{6}{8} \\
\ganttbar{Interactive Record \& Playback}{11}{14}\\
\ganttmilestone{First Prototype}{18}\\
\ganttbar{Collaborative Environment}{15}{18}\\
\ganttmilestone{Second Prototype}{22} \\
\ganttbar{Interface Improvement I}{19}{22} \\
\ganttbar{Usability Tests I}{23}{23} \\
\ganttmilestone{Third Prototype}{25} \\
\ganttbar{Interface Improvement II}{24}{25} \\
\ganttbar{Usability Tests II}{26}{26} \\
\ganttbar{Performance Tests}{29}{30} \\
\ganttbar{Performance Improvements}{30}{30} \\
\ganttmilestone{Final Prototype}{30}

%\ganttlink{elem8}{elem9}


\ganttlink{elem9}{elem10}
\ganttlink[link type=F-S]{elem11}{elem12}
\ganttlink{elem12}{elem13}
\ganttlink[link type=F-S]{elem13}{elem15}
\ganttlink[link type=F-S]{elem15}{elem17}
\ganttlink[link type=F-S]{elem17}{elem18}
\ganttlink[link type=F-S]{elem18}{elem20}
\ganttlink[link type=F-S]{elem20}{elem21}
\end{ganttchart}


%RP o que estás duas semanas a fazer no final? Porque não entregas após a escrita. Se é tempo para eu rever, então deveria haver outra fase para corrigires. Penso que podemos considerar que isso fica tudo dentro do ``writting''. Se quiseres aumenta.

%RP troca ``essay writting'' por ``thesis writting''

